---
title: "Problem Set 1 ECO375"
output:
  pdf_document: default
  html_notebook: default
---

Install and load required R packages.
```{r}
chooseCRANmirror(graphics=FALSE, ind=33)
library(car)
```

Load data.
```{r}
dataset <- read.table(file="C:\\Users\\Fatema\\Documents\\Third Year\\ECO375\\Problem Set 1\\wage2.txt", header=TRUE, sep=",")
```

List names of the data variables.
```{r}
names(dataset)
```

Keep data on wage, education, experience, IQ, and age.
```{r}
dataset <- subset(dataset, select = c("wage", "IQ", "educ", "exper", "age"))
```

Find average wage, education, work experience, and IQ in the sample. 
```{r}
summary(dataset)
```
Therefore, average wage is 957.9; average IQ is 101.3; average education is 13.47; average age is 33.08 in the sample.

What is the sample standard deviation of IQ in the sample?
```{r}
sd(dataset$IQ)
```

How many individuals in the sample have exactly 12 years of education?
```{r}
sum(dataset$educ==12)
```
There are 393 people with 12 years of education.

What is the maximum level of education anyone has in the sample?
From above, the maximum education level is 18 years. 

Run the regression equation and provide the output.
```{r}
Regression <- lm(formula = log(wage) ~ IQ + educ + exper + age, data = dataset)
summary(Regression)
```

```{r}
coeffs = coefficients(Regression)
coeffs
```

What is the estimated percentage increase in wage if education is increased by one year, holding the other factors constant?
```{r}
educinc <- 100*coeffs[3]
educinc
```
Wage will increase by approximately 5.1%.

What is the estimated percentage increase in wage if education is increased by one year and experience is decreased by one year, holding the other factors constant?
```{r}
increase = 100*coeffs[3] - 100*coeffs[4]
increase
```
Wage will increase by 3.78%

Your friend has 12 years of education, 10 years of work experience, an IQ of 100, and is 28 years old. Find his/her predicted ln(wage).
```{r}
prediction = coeffs[1] + coeffs[2]*100 + coeffs[3]*12 + coeffs[4]*10 + coeffs[5]*28
prediction
```
Her predicted ln(wage) is 6.602511.

What percentage of the variation in ln(wage) is explained by the four covariates?
That is the value of R^2 we see in h the regression ouput ie. 17%

Test the null hypothesis that education and experience has no e¤ect on ln(wage), using a 5% signifcance level.
```{r}
linearHypothesis(Regression, c("educ=0", "exper=0"))
```
We fail to reject that education and experience has no effect on ln(wage). 

